\textsc{Beyond the Iceberg Hypothesis: \\Opening the Black Box of Transport Costs}

### 2017-01-05 redaction/dhp_sept2016.tex
Changements texte

Our analysis of transportation costs consists in exploiting the difference between commodity-level export and import prices, as in \cite{hummels2007} (among others). The database we use to construct our measure of transport costs comes from US annual Imports of Merchandise provided by the Census bureau\footnote{More information available at: \url{http://www.census.gov/foreign-trade/reference/products/catalog/fl_imp.txt}}, spanning from 1974 to 2013. We first use customs values, quantities and freight costs to recover free-alongside (fas) and cost-insurance-fret (cif) prices, by goods, country of origin and transportation mode.\footnote{The related literature commonly refers to the fob price rather than the fas price. While both are closely related, we refer to the fas price as the price considered by the US Foreign Trade Statistics.} More precisely, the (unit) fas price is computed as the total ``customs value'' in the US trade statistics divided by the shipping weight; in other words, it is the price for one kg of the good net of transportation costs. The cif price is then computed as the sum of the customs value and freight charges, once again divided by the shipping weight. Our dependant variable is finally computed as the ratio of the cif price divided by the fas price. Higher than 1, the variable provides therefore with a measure of transport costs as a proportion of the good's price, an \emph{ad-valorem} equivalent. This is a quite standard and widespread strategy, as emphasized by \citet{anderson_wincoop_jel}.

@@

We use sectorial price data at the 3-digit level, even if the data of transportation costs is available at a more disaggregated level. As detailed below, the use of a nonlinear estimator triggers computational limitations that limit the level of possible detail, especially when covering a long period of time.\footnote{Yet, we ensure the robustness of these results by conducting the estimations at the 4-digit level for some selected years. The selected years for the 4-digit level estimations are: 1974, 1977, 1981, 1985, 1989, 1993, 1997, 2001, 2005, 2009, 2013. Comparing different levels of aggregation is useful to check differences and the presence of biases precisely due to aggregation. We thus obtain no substantial difference between the estimation results conducted at the 3 and 4-digit levels. Estimation results at the 4-digit classification level are reported in Appendix ??.} Depending on the considered year, this leaves us with around 200 sectors sectors, from approximately 200 countries of origin.

@@

\paragraph{The estimated equation} Our purpose is to provide estimates over time of the size of ad-valorem and additive costs among total transport costs. To do so, we start from the equation that expresses the price $p$ of a good $k$ paid by the importer (import, or cif) a function of the producer price $\widetilde{p}$ (export, or fas), given both per-kg ($t$) and ad-valorem ($\tau$) transport costs, according to:

@@

\begin{equation*}
\frac{p_{ik}}{\widetilde{p}_{ik}} -1 = \tau_{ik} -1 +\frac{t_{ik}}{ \widetilde{p}_{ikz}} \label{eq:base_estimee}
\end{equation*}

@@

\begin{equation*}
\frac{p_{ik}}{\widetilde{p}_{ik}}-1 =\tau_{i} \times \tau_{k} -1 +\frac{t_{i} + t_{k}}{ \widetilde{p}_{ikz}} \label{eq:theory_equation}
\end{equation*}

@@

The non-linearity of Equation (\ref{eq:equation0}) implies that it cannot be estimated using standard linear estimators. All estimates are thus performed using non-linear least squares.\footnote{The basis of the method is to approximate the model by a linear one and to refine the parameters by successive iterations. The intuitive criterion for convergence is that the sum of squares does not decrease from one iteration to the next. See \cite{Woolridge-Book-2001} for more details.} Yet, the use of a nonlinear estimator triggers computational limitations that limit the level of possible detail, especially when covering a long period of time. Confronted to this arbitrage, we retain the 3-digit level as our benchmark classification, even though data series are available at the 5-digit classification level ($k$). This drives us to estimate a modified version of Equation (\ref{eq:equation0}), according to:
\begin{equation}
\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)= \ln \left(\tau_{i} \times \tau_{s}+\frac{t_{i} + t_{s}}{\widetilde{p}_{ik}}-1 \right) + \epsilon_{ik} \label{eq:estimatedequation}
\end{equation}
where $\tau_{i}$, $\tau_{s}$, $t_{i}$ and $t_{s}$ are the parameters to be estimated, i.e., fixed effects specific to each origin country $i$ and sector $s$ (at the 3-digit classification level), and $\epsilon_{ik}$ the residual centered on 0. To eliminate the potential influence of outliers, we excluded 5 percent of the upper and lower tails of the distribution in the regression variables. These cut-offs are aimed at eliminating reporting or coding errors. We estimate this equation for each year over the period 1974-2013, for each of the transportation mode reported (air or vessel), on a sectoral-origin country basis ($i,s$). Depending on the year considered, this leaves us with around 800 fixed effects to estimate by transport mode (at the 3-digit level).   \smallskip

@@

\begin{eqnarray}
\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)&=& \ln \left(\tau_{i}\times\tau_{s}-1 \right) + \epsilon^{nlI}_{ik} \label{eq:model_nlI} \\
%\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)&=& \ln \left(\frac{t_{i} + t_{s}}{\widetilde{p}_{ik}}\right) + \epsilon^{nlA}_{ik} \label{eq:model_nlA} \\
\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)&=& \ln \left(\tau_{i} \times \tau_{s}-1 +\frac{t_{i} + t_{s}}{\widetilde{p}_{ik}}\right) + \epsilon_{ik} \label{eq:model_IetA}
\end{eqnarray}

After estimating Equation (\ref{eq:model_IetA}), we can re-built a measure of each component $\widehat{\tau}^{adv}_{is} = \widehat{\tau_{i}} \times \widehat{\tau_{s}}$ and $\widehat{t}^{add}_{is} = \widehat{t}_{i} + \widehat{t}_{s}$, that is country-product specific, by year and transport mode. Under Model (a), when assuming iceberg costs only (Equation (\ref{eq:model_nlI})), we proceed similarly to get $\widehat{\tau}^{nlI}_{is} = \widehat{\tau_{i}} \times \widehat{\tau_{s}}$.\footnote{In this case, notice that the equation could be estimated relying on a linear form. To preserve comparability of the results, we keep the same non-linear estimation method in both cases though.}$^{,}$\footnote{One may object that a comprehensive study of the structure of transport costs should also include the third model with only additive costs. This has driven us to estimate this case as well, in which case the estimated equation is written according to: $\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)= \ln \left(\frac{t_{i} + t_{s}}{\widetilde{p}_{ik}}\right) + \epsilon^{nlA}_{ik}$. The main result that emerges is that the model with additive costs only is dominated (in terms of quality of fit properties) by the model with multiplicative costs only (which is itself dominated by the complete model (b), anticipating on further results. For sake of space saving, the results of this model are not reported in the paper. Of course, they are available upon request to the authors.} Similarly as \citet{Irrazabal_2015}, we take the average over the product-country dimension, using the values of each trade flow ($is$-specific) over total yearly trade as a weighting scheme. We thus recover a ``synthetic estimate'' of each type of transport cost: \textit{a)} $\widehat{\tau}^{nlI}$, \textit{b)} $\widehat{\tau}^{adv}$ and $\widehat{t}$, for each year and transportation mode. These results are reported in Section \ref{sec:results_decomposition}.

@@

Our first contribution to the literature is to provide estimates for the size of both the ad-valorem and the additive components of transport costs. Table \ref{tab:summary_results} reports a summary of our results. It displays the mean and median values of each type of trade costs, as well as the associated standard deviation, averaged over the period 1974-2013, for estimation driven both at the 3- and 4-digit sectorial level for different specifications and data. The first panel reports the results for a specification based on ad-valorem costs estimated alone, while the second panel presents estimates for a specification involving both ad-valorem and multiplicative component. Finally, the third panel reports the same set of descriptive statistics, but for the actual cif/fas ratio in our data.\footnote{In Appendix \ref{app:more_results}, we report similar results for a sample of years, for both transport mode, at the 3 and 4-digit classification level. Results for all years (available at the 3-digit level) are available upon request to the authors.}$^{,}$\footnote{We present the results for air at the 3-digit level removing the year 1989, as the estimation results reveal the presence of strong outliers that bias the estimates of transport costs upwards. Overall results (over the whole period) are not substantially affected if this year is included though. These results are available upon request to the authors.}

@@

Table \ref{tab:summary_results} calls for two types of comments. Starting with pure statistical concerns, it appears that mean values are systematically higher than medians - by around one percentage point. This is no surprise at all: once again, our key variable is by nature bounded to 0; therefore, outliers can only be positive, pushing the mean up compared to the median. Besides, one can also note that estimated total costs are also systematically higher than observed costs by 0.5 to 1 percentage point. This is due to the fact that observed data are \emph{de facto} trade-weighted (i.e., by the weight of each good among total trade), while our estimates are based on simple arithmetic means - section 4 will go into more details of these compositions effects.

Coming now to interpretation, Table \ref{tab:summary_results} shows the magnitude of overall transport costs is sizeable. Over 1974-2013, they correspond to a mean increase of the export price by 5.8\% for ocean shipping, and by 5.1\% for air shipping. Furthermore, when decomposing transport costs into an additive and an ad-valorem component, we find that the per-kg cost dimension is sizeable. Over the whole period, additive costs are 2.9\% of the export price for ocean shipping  - and ad-valorem ones being equal to 3.2\%. These values are respectively equal to 1.8\% and 2.5\% for air transport. For both transport modes, the omission of the additive term seriously biases the ad-valorem term upward. In quantitative terms, the omission of the additive term leads to overestimate the ad-valorem component by roughly a factor 2.%\todo{Ajouter un commentaire sur mean different de median, en comparaison avec les data.}

@@

The overall trend pictured in these estimates is in line with the findings by \citet{Hummels_1999}, who point that the overall transport cost for the United States declined from 6 percent to 4 percent between 1974 and 1996. Our own results point to a total decrease from 6.9 to 4.2\% on average for the same years.\footnote{For the sole 1994 year, \citet{Hummels_2001} finds an all-commodities trade-weighted average transport cost of 3.8 percent of the fob. price for the United States }\todo{This has to be clarified: What data uses Hummels? Does he distinghuish at some point between air and vessel.  }

XXX but our contribution goes beyond: we distinguish in this trend what comes from additive, and what comes form iceberg XXX

First, the magnitude of transport costs is higher for ocean shipping than for air transport. This result holds considering ad-valorem costs alone (Figure \ref{fig:mult_alone_withadd}), as well as in presence of costs (Figure \ref{fig:decomp_TC_3d}), for all years throughout the period. Second, in both transport modes, the additive component appears of sizeable importance: As mean value over the period, it amounts to 48.2\% of total transport costs in Vessel, and 42.3\% in Air. We go on investigating this result further in the next subsection.\footnote{Figure \ref{fig:decomp_TC_3d} also delivers interesting results with respect to the time trends of transport costs. We come back to this aspect in Section \ref{sec:results_trends}.}

\todo{Comparer avec la litterature. Cf AvW 2004 pure transport costs 11\% markup over production costs.}

@@

\section{Some detailed results \label{app:more_results}}

In this section, we report the estimates for international transport costs, by transport mode on a yearly basis, when either additive costs are included in the estimation (Equation (\ref{eq:model_IetA})) or not (Equation (\ref{eq:model_nlI})). For sake of space saving, we only report the results for a sample of years. Tables \ref{tab:result_air_rob} and \ref{tab:result_ves_rob} display the results for the 4-digit product-level estimation (again, for selected years).

\begin{table}[htbp]
  \centering
  \caption{Air: Dynamics of Trade Costs over Time, 3 digits (selected years)}
\begin{center}
    \begin{tabular}{l|cccccc}
\hline\hline

Year & 1974  & 1980  & 1990  & 2000  & 2010  & 2013   \\ \hline
\multicolumn{7}{l}{\textbf{With only Iceberg Trade Costs}}     \\
Mean  & 1.069 & 1.054 & 1.050 & 1.036 & 1.042 & 1.034  \\
Median & 1.054 & 1.038 & 1.044 & 1.025 & 1.034 & 1.029  \\
Standard Error & 0.052 & 0.049 & 0.039 & 0.033 & 0.037 & 0.024 \\
\hline
\multicolumn{7}{l}{\textbf{With Additive \& Iceberg Trade Costs }}    \\
\multicolumn{1}{l}{\textit{Additive term }} &       &       &       &       &       &      \\
\multicolumn{1}{l}{Mean } & 0.026 & 0.020 & 0.018 & 0.013 & 0.011 & 0.010  \\
\multicolumn{1}{l}{Median} & 0.011 & 0.005 & 0.008 & 0.005 & 0.004 & 0.005  \\
\multicolumn{1}{l}{Standard Error} & 0.040 & 0.041 & 0.033 & 0.028 & 0.024 & 0.020  \\
\multicolumn{1}{l}{\textit{Iceberg term}} &       &       &       &       &       &        \\
\multicolumn{1}{l}{Mean } & 1.036 & 1.023 & 1.024 & 1.017 & 1.026 & 1.017  \\
\multicolumn{1}{l}{Median} & 1.027 & 1.016 & 1.016 & 1.012 & 1.022 & 1.017 \\
Standard Error & 0.032 & 0.025 & 0.021 & 0.016 & 0.023 & 0.012  \\ \hline
\# observations & 14955 & 16118 & 24958 & 35027 & 40279 & 39351  \\
\hline\hline
    \end{tabular}%
  \end{center}
  \label{tab:result_air_3d_detail}%
\tiny{Notes: Statistics are obtained weighting each observation by its value in transport (mode-dependent). Additive term expressed in fraction of fas price. }
\end{table}%

\begin{table}[htbp]
  \centering
  \caption{Vessel: Dynamics of Trade Costs over Time (3 digits), selected years}
\begin{center}
    \begin{tabular}{l|cccccc}
   \hline\hline
Year         & 1974  & 1980  & 1990  & 2000  & 2010  & 2013   \\
 \hline
   \textbf{With only Iceberg Trade Costs} &       &       &       &       &       &       \\
Mean  & 1.098 & 1.065 & 1.057 & 1.051 & 1.040 & 1.036  \\
Median & 1.096 & 1.055 & 1.046 & 1.049 & 1.036 & 1.033  \\
Standard Error & 0.053 & 0.040 & 0.032 & 0.028 & 0.020 & 0.018  \\
\textbf{With Additive \& Iceberg Trade Costs} &       &       &       &       &       &     \\
\hline
\textit{Additive term } &       &       &       &       &       &        \\
Mean  & 0.051 & 0.034 & 0.027 & 0.028 & 0.025 & 0.015  \\
Median & 0.029 & 0.023 & 0.017 & 0.022 & 0.019 & 0.008 \\
Standard Error & 0.085 & 0.046 & 0.040 & 0.043 & 0.025 & 0.020 \\
\textit{Iceberg term} &       &       &       &       &       &        \\
Mean  & 1.054 & 1.031 & 1.033 & 1.025 & 1.019 & 1.022 \\
Median & 1.049 & 1.024 & 1.028 & 1.021 & 1.018 & 1.018  \\
Standard Error & 0.041 & 0.023 & 0.022 & 0.021 & 0.018 & 0.018  \\
\hline
 \# obs & 19007 & 17356 & 28383 & 36090 & 37748 & 38473 \\ \hline
\hline\hline
    \end{tabular}%
  \end{center}
  \label{tab:result_ves_3d_detail}%
\tiny{Notes: Statistics are obtained weighting each observation by its value in transport (mode-dependent). Additive term expressed in fraction of fas price. }
\end{table}%

\begin{table}[htbp]
  \centering
  \caption{Air: Dynamics of Trade Costs over Time, 4-digit}
\begin{center}
    \begin{tabular}{l|cccccc}
   \hline\hline
Year & 1974  & 1981  & 1989  & 2001  & 2009  & 2013 \\
\multicolumn{7}{l}{\textbf{With only Iceberg Trade Costs} }  \\
Mean  & 1.066 & 1.058 & 1.052 & \multicolumn{1}{c}{1.033} & \multicolumn{1}{c}{1.037} & \multicolumn{1}{c}{1.032} \\
Median & 1.052 & 1.044 & 1.041 & \multicolumn{1}{c}{1.021} & \multicolumn{1}{c}{1.027} & \multicolumn{1}{c}{1.026}  \\
Standard Error & 0.056 & 0.054 & 0.046 & \multicolumn{1}{c}{0.040} & \multicolumn{1}{c}{0.036} & \multicolumn{1}{c}{0.025}  \\
\hline
\multicolumn{7}{l}{\textbf{With Additive \& Iceberg Trade Costs }}  \\ \hline
\textit{Iceberg term} &       &       &       &       &       &     \\
Mean  & 1.035 & 1.026 & 1.031 & \multicolumn{1}{c}{1.015} & \multicolumn{1}{c}{1.021} & \multicolumn{1}{c}{1.016}  \\
Median & 1.025 & 1.017 & 1.019 & \multicolumn{1}{c}{1.010} & \multicolumn{1}{c}{1.017} & \multicolumn{1}{c}{1.014}  \\
Standard Error & 0.036 & 0.028 & 0.030 & \multicolumn{1}{c}{0.021} & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.015}  \\
\textit{Additive term} &       &       &       &       &       &     \\
Mean  & 0.026 & 0.021 & 0.017 & \multicolumn{1}{c}{0.012} & \multicolumn{1}{c}{0.012} & \multicolumn{1}{c}{0.010} \\
Median & 0.012 & 0.006 & 0.006 & \multicolumn{1}{c}{0.005} & \multicolumn{1}{c}{0.004} & \multicolumn{1}{c}{0.004}  \\
Standard Error & 0.039 & 0.042 & 0.033 & \multicolumn{1}{c}{0.027} & \multicolumn{1}{c}{0.029} & \multicolumn{1}{c}{0.019} \\ \hline
\# obs & 14944 & 16844 & 25307 & \multicolumn{1}{c}{35005} & \multicolumn{1}{c}{38475} & \multicolumn{1}{c}{39460}  \\
\hline\hline
    \end{tabular}%
  \end{center}
  \label{tab:result_air_rob}%
\tiny{Notes:Statistics are obtained weighting each observation by its value in transport (mode-dependent). Additive term expressed in fraction of fas price. }
\end{table}%

>>>>

Our analysis of transportation costs consists in exploiting the difference between commodity-level export and import prices, as in \cite{hummels2007} (among others). The database we use to construct our measure of transport costs comes from US annual Imports of Merchandise provided by the Census bureau,\footnote{More information available at: \url{http://www.census.gov/foreign-trade/reference/products/catalog/fl_imp.txt}} spanning from 1974 to 2013. We first use customs values, quantities and freight costs to recover free-alongside (fas) and cost-insurance-fret (cif) prices, by goods, country of origin and transportation mode.\footnote{The related literature commonly refers to the fob price rather than the fas price. While both are closely related, we refer to the fas price as the price considered by the US Foreign Trade Statistics.} More precisely, the (unit) fas price is computed as the total ``customs value'' in the US trade statistics divided by the shipping weight; in other words, it is the price for one kg of the good net of transportation costs. The cif price is then computed as the sum of the customs value and freight charges, once again divided by the shipping weight. Our dependant variable is finally computed as the ratio of the cif price divided by the fas price. Higher than 1, the variable provides therefore with a measure of transport costs as a proportion of the good's price, an \emph{ad-valorem} equivalent. This is a quite standard and widespread strategy, as emphasized by \citet{anderson_wincoop_jel}.

@@

We estimate international transport costs at the 3-digit classification level, even if data series on the cif and fas prices are available at the 5-digit classification level. As detailed below, the use of a nonlinear estimator triggers computational limitations that limit the level of possible detail, especially when covering a long period of time. Yet, we ensure the robustness of these results by conducting the estimations at the 4-digit level for some selected years.\footnote{The selected years for the 4-digit level estimations are: 1974, 1977, 1981, 1985, 1989, 1993, 1997, 2001, 2005, 2009, 2013. Comparing different levels of aggregation is useful to check differences and the presence of biases precisely due to aggregation. We thus obtain no substantial difference between the estimation results conducted at the 3 and 4-digit levels. Estimation results at the 4-digit classification level are reported in Appendix ??.} Depending on the considered year, this leaves us with around 200 sectors, from approximately 200 countries of origin.

@@

\paragraph{The estimated equation} Our purpose is to provide estimates over time of the size of ad-valorem and additive costs among total transport costs. To do so, we start from the equation that expresses the price $p$ of a good paid by the importer (import, or cif price) as a function of the producer price $\widetilde{p}_{isk}$ (export, or fas price), given both per-kg ($t$) and ad-valorem ($\tau$) transport costs, according to:

@@

\begin{equation*}
\frac{p_{ik}}{\widetilde{p}_{ik}} -1 = \tau_{ik} -1 +\frac{t_{ik}}{ \widetilde{p}_{ik}} \label{eq:base_estimee}
\end{equation*}

@@

\begin{equation*}
\frac{p_{ik}}{\widetilde{p}_{ik}}-1 =\tau_{i} \times \tau_{k} -1 +\frac{t_{i} + t_{k}}{ \widetilde{p}_{ik}} \label{eq:theory_equation}
\end{equation*}

@@

The non-linearity of Equation (\ref{eq:equation0}) implies that it cannot be estimated using standard linear estimators. All estimates are thus performed using non-linear least squares.\footnote{The basis of the method is to approximate the model by a linear one and to refine the parameters by successive iterations. The intuitive criterion for convergence is that the sum of squares of residuals does not increase from one iteration to the next. See \cite{Woolridge-Book-2001} for more details.} Yet, the use of a nonlinear estimator triggers computational limitations that limit the level of possible detail, especially when covering a long period of time. Confronted to this arbitrage, we estimate international transport costs at the 3-digit level as our benchmark classification, even though data series are available at the 5-digit classification level ($k$). Put it differently, this amounts making the additional assumption, that all products $k$ in a 3-digit sector $s$ share the
same structure of costs.\footnote{We ensure the robustness of our estimation results to this assumption in two ways. First, we conduct the estimations at the 4-digit level for some selected years. As reported in Appendix \ref{app:4digit}, the results are not substantially affected. Second, we provide a decomposition variance exercise on the observed cif-fas price. As reported in Appendix ???, the share of the observed variance that is accounted for by the between-sector ($s$) variance is roughly similar to the between-product ($k$) variance.} This drives us to estimate a modified version of Equation (\ref{eq:equation0}), according to:
\begin{equation}
\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)= \ln \left(\tau_{i} \times \tau_{s(k)}+\frac{t_{i} + t_{s(k)}}{\widetilde{p}_{ik}}-1 \right) + \epsilon_{ik} \label{eq:estimatedequation}
\end{equation}
where $\tau_{i}$, $\tau_{s(k)}$, $t_{i}$ and $t_{s(k)}$ are the parameters to be estimated, i.e., fixed effects specific to each origin country $i$ and sector $s$ (at the 3-digit classification level), and $\epsilon_{ik}$ the residual centered on 0. To eliminate the potential influence of outliers, we excluded 5 percent of the upper and lower tails of the distribution in the regression variables. These cut-offs are aimed at eliminating reporting or coding errors. We estimate this equation for each year over the period 1974-2013, for each of the transportation mode reported (air or vessel), on a sectoral-origin country basis ($i,s$). Depending on the year considered, this leaves us with around 800 fixed effects to estimate by transport mode (at the 3-digit level).   \smallskip

@@

\begin{eqnarray}
\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)&=& \ln \left(\tau_{i}\times\tau_{s(k)}-1 \right) + \epsilon^{nlI}_{ik} \label{eq:model_nlI} \\
%\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)&=& \ln \left(\frac{t_{i} + t_{s}}{\widetilde{p}_{ik}}\right) + \epsilon^{nlA}_{ik} \label{eq:model_nlA} \\
\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)&=& \ln \left(\tau_{i} \times \tau_{s(k)}-1 +\frac{t_{i} + t_{s}}{\widetilde{p}_{ik}}\right) + \epsilon_{ik} \label{eq:model_IetA}
\end{eqnarray}

After estimating Equation (\ref{eq:model_IetA}), we can re-built a measure of each component $\widehat{\tau}^{adv}_{is(k)} = \widehat{\tau_{i}} \times \widehat{\tau_{s(k)}}$ and $\widehat{t}^{add}_{is(k)} = \widehat{t}_{i} + \widehat{t}_{s(k)}$, that is country-sector specific, by year and transport mode. When assuming iceberg costs only (Equation (\ref{eq:model_nlI})), we proceed similarly to get $\widehat{\tau}^{nlI}_{is(k)} = \widehat{\tau_{i}} \times \widehat{\tau_{s(k)}}$.\footnote{In this case, notice that the equation could be estimated relying on a linear form. To preserve comparability of the results, we keep the same non-linear estimation method in both cases though.}$^{,}$\footnote{One may object that a comprehensive study of the structure of transport costs should also include the third model with only additive costs. This has driven us to estimate this model as well, in which case the estimated equation is written according to: $\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)= \ln \left(\frac{t_{i} + t_{s(k)}}{\widetilde{p}_{ik}}\right) + \epsilon^{nlA}_{ik}$. The main result that emerges is that the model with additive costs only is dominated (in terms of quality of fit properties) by the model with multiplicative costs only (Equation (\ref{eq:model_nlI})), which is itself dominated by the complete model (Equation (\ref{eq:model_IetA})), anticipating on further results. For sake of space saving, the results of this model are not reported in the paper. Of course, they are available upon request to the authors.} Similarly as \citet{Irrazabal_2015}, we take the average over the product-country dimension, using the values of each trade flow ($is$-specific) over total yearly trade as a weighting scheme. We thus recover a ``synthetic estimate'' of each type of transport cost: \textit{a)} $\widehat{\tau}^{nlI}$, \textit{b)} $\widehat{\tau}^{adv}$ and $\widehat{t}$, for each year and transportation mode. These results are reported in Section \ref{sec:results_decomposition}.

@@

Our first contribution to the literature is to provide estimates for the size of both the ad-valorem and the additive components of transport costs. Table \ref{tab:summary_results} reports a summary of our results. It displays the mean and median values of each type of trade costs (ad-valorem estimated alone, estimated along with additive costs and the additive component), as well as the associated standard deviation, averaged over the period 1974-2013, for estimation driven both at the 3- and 4-digit sectorial level.\footnote{In Appendix \ref{app:more_results}, we report similar results for a sample of years, for both transport mode, at the 3 and 4-digit classification level. Results for all years (available at the 3-digit level) are available upon request to the authors. We investigate the evolution of transport costs over the period in more details in Section \ref{sec:results_decomposition}.}$^{,}$\footnote{We present the results for air at the 3-digit level removing the year 1989, as the estimation results reveal the presence of strong outliers that bias the estimates of transport costs upwards. Overall results (over the whole period) are not substantially affected if this year is included though. These results are available upon request to the authors.}

@@

Table \ref{tab:summary_results} yields the following comments. First, the magnitude of overall transport costs is sizeable. Over 1974-2013, they correspond to a mean increase of the export price by 5.8\% for ocean shipping, and by 5.1\% for air shipping. Air transport costs are smaller than sea transport costs. This is counter-intuitive, but certainly linked to selection effects.

Second, when decomposing transport costs into an additive and an ad-valorem component, we find that the per-kg cost dimension is sizeable. Over the whole period, additive costs are 2.9\% of the export price for ocean shipping  - and ad-valorem ones being equal to 3.2\%. These values are respectively equal to 1.8\% and 2.5\% for air transport. For both transport modes, the omission of the additive term seriously biases the ad-valorem term upward. In quantitative terms, the omission of the additive term leads to overestimate the ad-valorem component by roughly a factor 2.\todo{Ajouter un commentaire sur mean different de median, en comparaison avec les data.}

@@

At this stage, two interesting comments can be made. First, the magnitude of transport costs is higher for ocean shipping than for air transport. This result holds considering ad-valorem costs alone (Figure \ref{fig:mult_alone_withadd}), as well as in presence of costs (Figure \ref{fig:decomp_TC_3d}), for all years throughout the period. Second, in both transport modes, the additive component appears of sizeable importance: As mean value over the period, it amounts to 48.2\% of total transport costs in Vessel, and 42.3\% in Air. We go on investigating this result further in the next subsection.\footnote{Figure \ref{fig:decomp_TC_3d} also delivers interesting results with respect to the time trends of transport costs. We come back to this aspect in Section \ref{sec:results_trends}.}\todo{Comparer avec la litterature. Cf AvW 2004 pure transport costs 11\% markup over production costs.}

@@

\section{More on the estimation results \label{app:more_results}}

In this section, we report more detailed results for the estimates for international transport costs, by transport mode on a yearly basis, when either additive costs are included in the estimation (Equation (\ref{eq:model_IetA})) or not (Equation (\ref{eq:model_nlI})).

\subsection{Detailed results at the 3-digit classification level}

In this section, we complement the results displayed in Table \ref{tab:summary_results} by reporting the estimates of international transport costs for a sample of years over 1974-2013, when the degree of classification retained ($s$) is at the 3-digit classification level. Table \ref{tab:result_air_3d_detail} reports the results for Air transport. The results for Ocean transport are displayed in Table \ref{tab:result_ves_3d_detail}.

\begin{table}[htbp]
  \centering
  \caption{Air: Transport costs estimates, 3-digits (selected years)}
\begin{center}
    \begin{tabular}{l|cccccc}
\hline\hline

Year & 1974  & 1980  & 1990  & 2000  & 2010  & 2013   \\ \hline
\multicolumn{7}{l}{\textbf{With only Iceberg Trade Costs}}     \\ \hline
Mean  & 1.069 & 1.054 & 1.050 & 1.036 & 1.042 & 1.034  \\
Median & 1.054 & 1.038 & 1.044 & 1.025 & 1.034 & 1.029  \\
Standard Error & 0.052 & 0.049 & 0.039 & 0.033 & 0.037 & 0.024 \\
\hline
\multicolumn{7}{l}{\textbf{With Additive \& Iceberg Trade Costs }}    \\ \hline
\multicolumn{7}{l}{\textit{Additive term }}     \\ \hline
\multicolumn{1}{l}{Mean } & 0.026 & 0.020 & 0.018 & 0.013 & 0.011 & 0.010  \\
\multicolumn{1}{l}{Median} & 0.011 & 0.005 & 0.008 & 0.005 & 0.004 & 0.005  \\
\multicolumn{1}{l}{Standard Error} & 0.040 & 0.041 & 0.033 & 0.028 & 0.024 & 0.020  \\ \hline
\multicolumn{7}{l}{\textit{Iceberg term}}  \\ \hline
\multicolumn{1}{l}{Mean } & 1.036 & 1.023 & 1.024 & 1.017 & 1.026 & 1.017  \\
\multicolumn{1}{l}{Median} & 1.027 & 1.016 & 1.016 & 1.012 & 1.022 & 1.017 \\
Standard Error & 0.032 & 0.025 & 0.021 & 0.016 & 0.023 & 0.012  \\ \hline
\# observations & 14955 & 16118 & 24958 & 35027 & 40279 & 39351  \\
\hline\hline
\multicolumn{7}{l}{\parbox[l]{11cm}{ \vspace{7pt}\scriptsize{Notes: Statistics are obtained weighting each observation by its value in transport (mode-dependent). Additive term expressed in fraction of fas price.}}}
\end{tabular}%
\end{center} 
\label{tab:result_air_3d_detail}
\end{table}%

\begin{table}[htbp]
  \centering
  \caption{Vessel: Dynamics of Trade Costs over Time (3 digits), selected years}
\begin{center}
    \begin{tabular}{l|cccccc}
   \hline\hline
Year         & 1974  & 1980  & 1990  & 2000  & 2010  & 2013   \\
 \hline
   \multicolumn{7}{l}{\textbf{With only Iceberg Trade Costs} }  \\
Mean  & 1.098 & 1.065 & 1.057 & 1.051 & 1.040 & 1.036  \\
Median & 1.096 & 1.055 & 1.046 & 1.049 & 1.036 & 1.033  \\
Standard Error & 0.053 & 0.040 & 0.032 & 0.028 & 0.020 & 0.018  \\
\multicolumn{7}{l}{\textbf{With Additive \& Iceberg Trade Costs} }    \\
\hline
\multicolumn{7}{l}{\textit{Additive term } }  \\ \hline
Mean  & 0.051 & 0.034 & 0.027 & 0.028 & 0.025 & 0.015  \\
Median & 0.029 & 0.023 & 0.017 & 0.022 & 0.019 & 0.008 \\
Standard Error & 0.085 & 0.046 & 0.040 & 0.043 & 0.025 & 0.020 \\ \hline
\multicolumn{7}{l}{\textit{Iceberg term} } \\ \hline
Mean  & 1.054 & 1.031 & 1.033 & 1.025 & 1.019 & 1.022 \\
Median & 1.049 & 1.024 & 1.028 & 1.021 & 1.018 & 1.018  \\
Standard Error & 0.041 & 0.023 & 0.022 & 0.021 & 0.018 & 0.018  \\
\hline
 \# obs & 19007 & 17356 & 28383 & 36090 & 37748 & 38473 \\ \hline
\hline\hline
\multicolumn{7}{l}{\parbox[l]{11cm}{ \vspace{7pt}\scriptsize{Notes: Statistics are obtained weighting each observation by its value in transport (mode-dependent). Additive term expressed in fraction of fas price.}}}
\end{tabular}%
\end{center} \label{tab:result_ves_3d_detail}
\end{table}%

\subsection{Estimation at the 4-digit level \label{app:4digit}}

In this section, we report the estimation results when we retain the 4-digit classification level ($s$=4-digit).

\paragraph{Transport cost estimates} Tables \ref{tab:result_air_rob} and \ref{tab:result_ves_rob} report the estimates of both models (with and without additive costs) in Air and Ocean transport respectively.
